### 2023-06-02 python_excel_ite.tex
module positioning

\section{Module structure}

\section{The modeling notebooks}
\subsection{Notebook 1: Modeling and data tables}
\subsection{Notebook 2: Goal seek}
\subsection{Notebook 3: Monte-Carlo simulation}

\section{The packaging notebooks}
\subsection{Notebook 4: Project packaging}
\subsection{Notebook 5: Documentation}

\section{The wrangling notebooks}
\subsection{Notebook 6: Manipulating Excel files with Python}

>>>>

\section{Module positioning and structure}

What kind of Python background do students need have in order to be ready for this EwP module? This module does presume a basic familiarity with Python fundamentals for data analysis such as:

\begin{itemize}
	\item variables, artithmetic and boolean operators, and basic data types,
	\item data structures such as lists, dictionaries, tuples, NumPy arrays and pandas dataframes,
	\item flow control such as branching with \texttt{if \ldots else} and looping with \texttt{for} and \texttt{while}
	\item module imports,
	\item using built in functions and accessing methods and properties of objects,
	\item creating functions,
	\item basic use of NumPy and pandas for data wrangling and analysis,
	\item basic plotting with matplotlib.
\end{itemize}

The EwP module could easily be used as part of a semester long Python based analytics course. At our institution, this module is part of a business course entitled "Advanced Analytics with Python" (\href{http://www.sba.oakland.edu/faculty/isken/courses/mis6900}{AAP}). The students taking this course have already taken my "Practical Computing for Business Analytics" (\href{http://www.sba.oakland.edu/faculty/isken/courses/mis5470}{PCDA}) course in which they spend about half the semester learning R and the other half learning Python, both in the context of business analytics. Some Linux basics are also part of the PCDA course. The students have also already taken "Business Analytics" (\href{http://www.sba.oakland.edu/faculty/isken/courses/mis5460}{BA}) which is a spreadsheet based introduction to business analytics. The BA and PCDA courses have historically been offered in face to face mode in a computer teaching lab. Since 2020, these two courses have been also offered as online, asynchronous courses. The newer AAP course has been offered since 2021 in an online asynchronous mode. All three courses have extensive course websites that are publicly accessible, including access to all of the video content and files needed. We will describe the AAP course web in more detail below in the context of the EwP module.

The EwP module is made of three submodules. The first of these focuses on building and using typical spreadsheet model using Python

\section{Submodule 1: The modeling notebooks}

\subsection{Notebook 1: Modeling and data tables}
\subsection{Notebook 2: Goal seek}
\subsection{Notebook 3: Monte-Carlo simulation}

\section{Submodule 2: The packaging notebooks}
\subsection{Notebook 4: Project packaging}
\subsection{Notebook 5: Documentation}

\section{Submodule 3: The wrangling notebook}
\subsection{Notebook 6: Manipulating Excel files with Python}
